Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
Puntuacion añadida en las figuras
Escenarios en AWS como lista

The first scenarion (Figure~\ref{subfig:aws1}) shows the most common 
and used hardware configuration in real clusters, where each node is 
populated with one GPU. Here, a simple node is able to use up to 5 GPUs 
using the ``High'' interconnection.

The second configuration (Figure~\ref{subfig:aws2}) is composed by 2 server nodes equipped 
with 4 GPUs each one and a client that does not have any GPU. This scenario is using 
a 10Gb network and the cliend is able to execute application using up to 8 GPUs.

The last scenario (Figure~\ref{subfig:aws3}), joins both previous ones and a single client, 
using a 1Gb network interconnection has 13 GPUs that can be used as if they were locally installed.

@@

Moreover, with the aim to know the expected network bandwidth using 
a remote GPU, we have executed again the NVIDIA {\tt bandwidthtest} sample.
The results observed in the Table~\ref{} shows how the bandwidth achieved is limited 
by the network.

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using {rCUDA}.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Scenario &  Data Movement & Network & BandWidth \\ \hline \hline
A & Host to Device & Hight& 127 MB/s \\ \hline
A & Device to Host & Hight& 126 MB/s\\ \hline
B & Host to Device & 10 Gb& 858 MB/s\\ \hline
B & Device to Host & 10 Gb& 843 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure}[htb]
\centering
\subfigure[first]{%
\includegraphics[width=\linewidth]{images/lammps100.png}
\label{subfig:lammps1}}
\quad
\subfigure[second]{%
\includegraphics[width=\linewidth]{images/lammps2000.png}
\label{subfig:lammps2}}
\caption{Execution time of LAMMPS}
\label{fig:lammps}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os-orig.png}
  \caption{Openstack Architecture}
  \label{fig:os-orig}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os1.jpg}
  \caption{Openstack with our GPGPU Service}
  \label{fig:external}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os2.png}
  \caption{Internal Communication among modules}
  \label{fig:internal}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=.5\textwidth]{images/workingmodes.jpg}
  \caption{Examples of working modes}
  \label{fig2}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/UI-launch.pdf}
  \caption{Launching Instances and assigning GPUs}
  \label{fig:ui-launch}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/UI-rgpus.pdf}
  \caption{GPU Information Panel}
  \label{fig:ui-rgpus}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.5\textwidth]{images/chart.jpg}
  \caption{Execution time of MCUDA-MEME}
  \label{fig3}
\end{figure}

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.

The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.

>>>>

\begin{itemize}
\item Scenario A (Figure~\ref{subfig:aws1}) shows the most common 
and used hardware configuration in real clusters, where each node is 
populated with one GPU. Here, a simple node is able to use up to 5 GPUs 
using the ``High'' interconnection.

\item Scenario B (Figure~\ref{subfig:aws2}) is composed by 2 server nodes equipped 
with 4 GPUs each one and a client that does not have any GPU. This scenario is using 
a 10Gb network and the cliend is able to execute application using up to 8 GPUs.

\item Scenario C (Figure~\ref{subfig:aws3}), joins both previous ones and a single client, 
using a 1Gb network interconnection has 13 GPUs that can be used as if they were locally installed.
\end{itemize}

@@

Moreover, with the aim to know the expected network bandwidth using 
a remote GPU, we have executed again the NVIDIA {\tt bandwidthtest} sample.
The results observed in the Table~\ref{table:bwtrcuda} shows how the bandwidth achieved is limited 
by the network.

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using {rCUDA}.}
\label{table:bwtrcuda}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Scenario &  Data Movement & Network & BandWidth \\ \hline \hline
A & Host to Device & Hight& 127 MB/s \\ \hline
A & Device to Host & Hight& 126 MB/s\\ \hline
B & Host to Device & 10 Gb& 858 MB/s\\ \hline
B & Device to Host & 10 Gb& 843 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure}[htb]
\centering
\subfigure[first]{%
\includegraphics[width=\linewidth]{images/lammps100.png}
\label{subfig:lammps1}}
\quad
\subfigure[second]{%
\includegraphics[width=\linewidth]{images/lammps2000.png}
\label{subfig:lammps2}}
\caption{Execution time of LAMMPS.}
\label{fig:lammps}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os-orig.png}
  \caption{Openstack Architecture.}
  \label{fig:os-orig}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os1.jpg}
  \caption{Openstack with our GPGPU Service.}
  \label{fig:external}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os2.png}
  \caption{Internal Communication among modules.}
  \label{fig:internal}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=.5\textwidth]{images/workingmodes.jpg}
  \caption{Examples of working modes.}
  \label{fig2}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/UI-launch.pdf}
  \caption{Launching Instances and assigning GPUs.}
  \label{fig:ui-launch}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/UI-rgpus.pdf}
  \caption{GPU Information Panel.}
  \label{fig:ui-rgpus}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.5\textwidth]{images/chart.jpg}
  \caption{Execution time of MCUDA-MEME.}
  \label{fig3}
\end{figure}

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.
The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.
